Large squeezing in Bose-Einstein condensates with large numbers of atoms

### 2013-07-12 large_number_squeezing_with_atoms.tex
Fix figure 3, minor appendix tweaks

\appendix
\section{Derivation of two mode squeezing formula}
\label{appendixTwoModeDerivation}
In this Appendix we derive the equations for the number variances. We use the model described in Section \ref{secTwoModeAnalytic}, where we consider a two mode system with $N$ particles, initially prepared as a coherent state with all the population in mode $|a\rangle$ at time $t=0$. A coupling pulse is then applied, so that the system evolves under the Hamiltonian
\begin{equation}
\hat{H_1} = \hbar \omega \hat{a}^{\dagger} \hat{a} +  \hbar \omega \hat{b}^{\dagger} \hat{b} 
          + \hbar \Omega (\hat{a}^{\dagger} \hat{b} + \hat{b}^{\dagger} \hat{a} )
\end{equation}
until time $t=t_1$. From time $t_1$ until time $t=t_2$ the coupling is turned off, and the system evolves under the Hamiltonian
\begin{equation}
\hat{H_2} = \hbar\frac{\chi_{aa}}{2} \hat{a}^{\dagger} \hat{a}^{\dagger} \hat{a} \hat{a}
          + \hbar\chi_{ab} \hat{a}^{\dagger} \hat{a} \hat{b}^{\dagger} \hat{b}
          + \hbar\frac{\chi_{bb}}{2} \hat{b}^{\dagger} \hat{b}^{\dagger} \hat{b} \hat{b}.
\end{equation}
Finally, from time $t_2$ until time $t=t_3$, the coupling is once again applied with a phase offset of $\phi$ relative to the first time, and the system evolves via
\begin{equation}
\hat{H_3} = \hbar \omega \hat{a}^{\dagger} \hat{a} +  \hbar \omega \hat{b}^{\dagger} \hat{b}
          + \hbar\Omega (e^{i\phi} \hat{a}^{\dagger} \hat{b} + e^{-i\phi} \hat{b}^{\dagger} \hat{a} ).
\end{equation}
It is clear that the linear self-energy terms proportional to $\omega$ result in a constant phase rotation of the fields $\hat{a}$ and $\hat{b}$. As this system is self-contained and global phase is unmeasurable, all phase measurements can only rely on the difference in phase between the two modes. This phase rotation is therefore irrelevant and will be ignored in the following analysis.

@@

Next we tackle $\langle \hat{a}^{\dagger}_2 \hat{a}^{\dagger}_2 \hat{b}_2 \hat{b}_2 \rangle$. Using (\ref{eqa2}) and (\ref{eqb2}) and the fact that $\hat{a}$ and $\hat{b}$ commute, we have

>>>>

\appendix
\section{Derivation of two mode squeezing formula}
\label{appendixTwoModeDerivation}
In this Appendix we derive the equations for the number variances. We use the model described in Section \ref{secTwoModeAnalytic}, where we consider a two mode system with $N$ particles, initially prepared as a coherent state with all the population in mode $|a\rangle$ at time $t=0$. A coupling pulse is then applied, assumed to be on resonance, so that the system evolves under the Hamiltonian
\begin{equation}
\hat{H_1} = \hbar \Omega (\hat{a}^{\dagger} \hat{b} + \hat{b}^{\dagger} \hat{a} )
\end{equation}
until time $t=t_1$. From time $t_1$ until time $t=t_2$ the coupling is turned off, and the system evolves under the Hamiltonian
\begin{equation}
\hat{H_2} = \hbar\frac{\chi_{aa}}{2} \hat{a}^{\dagger} \hat{a}^{\dagger} \hat{a} \hat{a}
          + \hbar\chi_{ab} \hat{a}^{\dagger} \hat{a} \hat{b}^{\dagger} \hat{b}
          + \hbar\frac{\chi_{bb}}{2} \hat{b}^{\dagger} \hat{b}^{\dagger} \hat{b} \hat{b}.
\end{equation}
Finally, from time $t_2$ until time $t=t_3$, the coupling is once again applied with a phase offset of $\phi$ relative to the first time, and the system evolves via
\begin{equation}
\hat{H_3} = \hbar\Omega (e^{i\phi} \hat{a}^{\dagger} \hat{b} + e^{-i\phi} \hat{b}^{\dagger} \hat{a} ).
\end{equation}

@@

We now consider $\langle \hat{a}^{\dagger}_2 \hat{a}^{\dagger}_2 \hat{b}_2 \hat{b}_2 \rangle$. Using (\ref{eqa2}) and (\ref{eqb2}) and the fact that $\hat{a}$ and $\hat{b}$ commute, we have
